Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Better bound on OPT
xspace

\usepackage[utf8]{inputenc}
%\usepackage{xspace}
\usepackage{balance}
\usepackage{amsmath,amsfonts,mathtools,amsthm}
\usepackage{algorithmic}
\usepackage{algorithm}

@@

\newcommand{\OPT}{\mathit{OPT}}
\newcommand{\ALG}{ALG}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\TAlg}{{\ensuremath{ALG_{k=3}}}} % we should change this name

@@

  %First, we estimate the cost related to $\sigma_I$.
  We have $OPT(M) + OPT(\sigma_I) \geq \alpha$, as the components of \TAlg{} could not be partitioned without splitting them, and there exist a pair of nodes with at least $\alpha$ requests between them.
  $\OPT$ either served them remotely or performed a migration.
  We obtain $\OPT \geq \max\{\alpha, \OPT(\sigma_E) + \OPT(M)}$.

@@

  Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ related to $\sigma_E$.

  Second, we estimate the cost related to $\sigma_E$.
  Now we bound the cost that $\OPT$ incurred while serving requests $\sigma_E$.
  If $\OPT$ would

  Now we bound the competitive ratio.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{balance}
\usepackage{amsmath,amsfonts,mathtools,amsthm}
\usepackage{algorithmic}
\usepackage{algorithm}

@@

\newcommand{\OPT}{\mathit{OPT}}
\newcommand{\ALG}{ALG}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\TAlg}{{\ensuremath{ALG_{k=3}}}\xspace} % we should change this name

@@

  %First, we estimate the cost related to $\sigma_I$.
  We have $OPT(M) + OPT(\sigma_I) \geq \alpha$, as the components of \TAlg{} could not be partitioned without splitting them, and there exist a pair of nodes with at least $\alpha$ requests between them.
  $\OPT$ either served them remotely or performed a migration.
  We obtain $\OPT \geq \max\{\alpha, \OPT(\sigma_E) + \OPT(M)\}$.

@@

  \maciek{unfinished, don't read :)}

  Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ with respect to $\sigma_E$.
  We begin by lower-bounding the number of requests from $\sigma_E$ that $\OPT$ must account (by either serving remotely or migrating), and we denote their number by $x$.
  It holds that $x \geq \TAlg(\sigma_E) - 3\cdot\ell\cdot(\alpha - 1)$, as it received all the requests that \TAlg did, but it could ignore the cost of serving at most $3\cdot\ell$ pairs of nodes, as it might have them collocated in its clusters.
  Each such pair of nodes account for at most $\alpha-1$ requests (the pairs from $\sigma_E$ are unsaturated) in the cost of $\TAlg(\sigma_E)$, hence collocating them would decrease the number by at most $3\cdot\ell\cdot(\alpha - 1)$.

  Now we bound the cost that $\OPT$ pays while serving these $x$ requests.
  Instead of serving all of them remotely, $\OPT$ can perform migrations to decrease its cost.
  By performing a swap of nodes $(u,v)$, $\OPT$ collocates $u$ with two nodes $u', u''$, and $v$ with two nodes $v'$, $v''$.
  (express that between a pair of nodes we accounted $\alpha-1$ requests in $x$)
  Hence, by performing a migration for the cost $\alpha$, $\OPT$ does not pay the remote serving costs for at most $4\cdot (\alpha - 1)$ requests from $x$ ($x$ is not a sequence but its length!).
  Finally, for serving $x$, $\OPT$ pays at least $x \cdot \frac{\alpha}{4\cdot (\alpha-1)}$.
  This gives us
  \begin{align*}
    \OPT(\sigma_E) + \OPT(M) & \geq (\TAlg(\sigma_E)-3\cdot\ell\cdot(\alpha - 1)) \cdot \frac{\alpha}{4\cdot (\alpha-1)}\\
    &\geq ...
  \end{align*}
